% Max 1 page
\iffalse
\begin{itemize}
	\item Critique
	\item Discussion
	\item Do not make the reader do all the work
\end{itemize}
\fi
%TODO: Write more here

\section{Future Work}
%% UX designer
The most focal point regarding future work to be done on this IoT scale is to involve an end-user in some shape or form early on. Ideally, a UX-designer would lead some form of market research study to more accurately specify what needs and requirements this kind of device would need to satisfy. This would be used to guide any further modifications and limitations put on the device.
%% Proper hardware assembly analysis
A more proper analyze of the needed hardware components needs to be done. Optimization in the form of hardware space, energy consumption and economical costs are essential if any more than a handful of devices are to be produced.
%% Standardized software solution
A more UX and design related question would pertain how standardized the software of the device needs to be constructed. Depending on how the use cases and market needs, can one solution fit all, or is there a way to tailor to needs in an effective way?
%% Pilot period


While the predictions and promises for the IoT industry remain hopeful and grandeur, no new devices and products will appear from thin air and propel IoT into being an integral pillar to our modern society just like that. The technology available today enables smarter products that have the potential to vastly improve our lives so long as we keep testing, trying, failing and improving. This paper was one, albeit small, test of these new technologies and many exciting projects are sure to come.